### 2017-07-07 paper.tex
Commenting on file formats being an extra obstacle.
Closes #36.

Tools can help,
especially if they allow proposed changes to be viewed and discussed
prior to their incorporation into the lessons.
(In software development this is known as ``pre-merge review''.)
However,
some tools that are popular in open source software development have considerable up-front learning costs.
Portals like GitHub,
for example,
support everything that open lesson development needs,
but require contributors to use Git,
which has a notoriously steep learning curve \cite{git-survey}.
Google Docs and wikis do not support pre-merge review,
but their low barrier to entry make them more welcoming to newcomers.

@@

>>>>

Tools can help,
especially if they allow proposed changes to be viewed and discussed
prior to their incorporation into the lessons.
(In software development this is known as ``pre-merge review''.)
However,
some tools that are popular in open source software development have considerable up-front learning costs.
Portals like GitHub,
for example,
support everything that open lesson development needs,
but require contributors to use Git,
which has a notoriously steep learning curve \cite{git-survey}.

Complicating matters further,
some file formats make collaboration easier or more difficult.
Despite their ubiquity,
open source version control systems do not directly support review or merge
of Microsoft Office or LibreOffice file formats,
which raises an additional burden for newcomers \cite{jacobs}.
Programmers may look down on Google Docs and wikis
for their lack of pre-merge review and other capabilities,
but their low barrier to entry make them more welcoming to newcomers.

@@

\bibitem{jacobs}
Jacobs C.~T., Gorman G.~J., Rees H.~E., and Craig L.~E.:
Experiences With Efficient Methodologies for Teaching Computer Programming to Geoscientists
\newblock Journal of Geoscience Education
\newblock 64(3),
\newblock 2016,
\newblock https://doi.org/10.5408/15-101.1
